---
name: Bruno Testaguzza Carlin
position: "Data Analyst"
address: "Bayer - São Paulo"
phone: +55 11 99376-5775
www: twosidesdata.netlify.com/
email: "brunotestaguzza@gmail.com"
twitter: BrunoTestaguzza
github: brunocarlin
linkedin: bruno-carlin-451007172
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Education

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates,
  "Post-graduate Degree Data Science and Decisions", "Insper", "São Paulo, Brasil", "Jun. 2019 - Mar 2021",
  "Course Data Science", "Digital House", "São Paulo, Brasil", "Feb. 2019 - May. 2019",
  "Enonomics", "Insper", "São Paulo, Brasil", "Jan. 2014 - Dec. 2018",
  "Foreign Commerce", "Porto Seguro", "São Paulo, Brasil", "Jan. 2011 - Dec. 2013",
) %>% 
  detailed_entries(degree, dates, uni, loc)
```


<!-- [Post-graduate Degree Data Science and Decisions](https://www.insper.edu.br/pos-graduacao/programas-avancados/programa-avancado-em-data-science-e-decisao/) -->

<!-- [Graduation Economics](https://www.insper.edu.br/graduacao/economia/) -->

<!-- [Studying Data Science](https://br.digitalhouse.com/curso/data-science/) -->

<!-- [Foreign Commerce - High School](https://www.portoseguro.org.br/conteudo/detalhe/currculo-brasileiro/ensino-mdio-comrcio-exterior) -->


# Experience

```{r experience}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Account Receivables Data Analyst", "Bayer", "São Paulo, Brasil", "Jan. 2020 - Present",
  "Developing the new Credit Model.",
  
  "Account Receivables Data Analyst", "Bayer", "São Paulo, Brasil", "Jan. 2020 - Present",
  "Responsible for multiple adhoc solutions delivering quick results to the business employing programming scripts to process small to medium size problem effectively and reliably.",
  
  "Account Receivables Data Analyst", "Bayer", "São Paulo, Brasil", "Jan. 2020 - Present",
  "Data Analysis on accounts receivables and revenues datasets, implementing pipelines from data extraction to dashboards",
  
  "Account Receivables Data Analyst", "Bayer", "São Paulo, Brasil", "Jan. 2020 - Present",
  "Critical Participant of a diverse array of projects like the DataGis of the Credit Area and the Online Financing tool.",
  
  "Credit Analyst", "Bayer", "São Paulo, Brasil", "Set. 2019 - Dec. 2020",
  "Financial analysis",
  
  
  "Credit Analyst", "Bayer", "São Paulo, Brasil", "Set. 2019 - Dec. 2020",
  "Adhoc scripts for data analysis",
  
  
  "Credit Analyst", "Bayer", "São Paulo, Brasil", "Set. 2019 - Dec. 2020",
  "Starting the machine learning Credit Model project",
  
  "Data Science Consultant", "Driven Consultant", "São Paulo, Brasil", "Jul. 2019 - Set. 2019",
  "Developed the time series model for Days on Hand of the client.",
  
  "Data Science Consultant", "Driven Consultant", "São Paulo, Brasil", "Jul. 2019 - Set. 2019",
  "SQL queries for model construction, adhoc analysis and dashboards.",
  
  "Trainee", "EY", "São Paulo, Brasil", "Apr. 2019 - Jun. 2019",
  "Automation of large scale accounting projects using programming scripts",
  
  
  "Trainee", "EY", "São Paulo, Brasil", "Apr. 2019 - Jun. 2019",
  "Documentation and analysis of the whole SQL pipeline, delivering business understanding",
  
  "Intern Risk Managment - Reporting", "Bayer", "São Paulo, Brasil", "Jan. 2018 - Dec 2018",
  "Creation, automation and maintenance of several credit and cash flow reports",
  
  "Intern Risk Managment - Reporting", "Bayer", "São Paulo, Brasil", "Jan. 2018 - Dec 2018",
  "Creation and improvement of Dashboards",
  
  "Intern Risk Managment - Reporting", "Bayer", "São Paulo, Brasil", "Jan. 2018 - Dec 2018",
  "Forecasting project, using my own ensemble method of time series models to create hierachichal forecasts",
  
  
  
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Languages

## Portuguese

Native.

## English

Advanced.  

No certification, used regularly.


## German

Basic-Intermediary.  

B1 Certification

## Spanish

Basic.  

No Certification.


# Data Science Skills

Learning Data Science, following blogs, reading books, doing online and on site courses, watching conference videos and more.

Well versed into using the tidyverse for Data Analysis and Statistical Inference.

Multiple projects doing time series forecasts.

Work experience using and developing SQL queries.

Dashboard creation using Shiny.

Working knowledge of Git.

You can see my open source work on my Data Science blog [twosidesdata](twosidesdata.netlify.com).

# Technologies

## Programming Languages

* R
* SQL
* Python

## Dashboard Creation

* Shiny
* Tableau
* Power BI

## Office Stack

* Excel
* Power Point




