---
name: Bruno Testaguzza Carlin
position: "Data Scientist - Modeling"
address: "Stone - São Paulo"
phone: +55 11 99376-5775
www: twosidesdata.netlify.com/
email: "brunotestaguzza@gmail.com"
twitter: BrunoTestaguzza
github: brunocarlin
linkedin: bruno-carlin-451007172
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Education

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates,
  "Post-graduate Degree Data Science and Decisions", "Insper", "São Paulo, Brasil", "Jun. 2019 - Jun. 2021",
  "Course Data Science", "Digital House", "São Paulo, Brasil", "Feb. 2019 - May. 2019",
  "Enonomics", "Insper", "São Paulo, Brasil", "Jan. 2014 - Dec. 2018",
  "Foreign Commerce", "Porto Seguro", "São Paulo, Brasil", "Jan. 2011 - Dec. 2013",
) %>% 
  detailed_entries(degree, dates, uni, loc)
```


<!-- [Post-graduate Degree Data Science and Decisions](https://www.insper.edu.br/pos-graduacao/programas-avancados/programa-avancado-em-data-science-e-decisao/) -->

<!-- [Graduation Economics](https://www.insper.edu.br/graduacao/economia/) -->

<!-- [Studying Data Science](https://br.digitalhouse.com/curso/data-science/) -->

<!-- [Foreign Commerce - High School](https://www.portoseguro.org.br/conteudo/detalhe/currculo-brasileiro/ensino-mdio-comrcio-exterior) -->


# Experience

```{r experience}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  
  "Data Scientist - Modeling", "Stone", "São Paulo, Brasil", "Apr. 2021 - Present",
  "Develop data science models for the credit team at Stone",
  
  "Data Scientist - Modeling", "Stone", "São Paulo, Brasil", "Apr. 2021 - Present",
  "Develop studies and data analysis for the credit team at Stone",
  
  
  "Data Scientist - Modeling", "Stone", "São Paulo, Brasil", "Apr. 2021 - Present",
  "Develop business critical concession and retention logic for the credit team at Stone",
  
  
  "Finance Data Scientist Latam", "Bayer", "São Paulo, Brasil", "Aug. 2020 - Apr. 2021",
  "Develop data science models for the finance latam team.",
  
  "Finance Data Scientist Latam", "Bayer", "São Paulo, Brasil", "Aug. 2020 - Apr. 2021",
  "Project Leader or Participant as business representative on latam finance projects",
  
  "Finance Data Scientist Latam", "Bayer", "São Paulo, Brasil", "Aug. 2020 - Apr. 2021",
  "Reports maintenance  and development for latam finance",
  
  "Finance Data Scientist Latam", "Bayer", "São Paulo, Brasil", "Aug. 2020 - Apr. 2021",
  "Limited scope programming solutions for the latam finance team",
  
  "Account Receivables Data Analyst Latam", "Bayer", "São Paulo, Brasil", "Jan. 2020 - Jul. 2020",
  "Developing the new Credit Model.",
  
  "Account Receivables Data Analyst Latam", "Bayer", "São Paulo, Brasil", "Jan. 2020 - Jul. 2020",
  "Responsible for multiple adhoc solutions delivering quick results to the business employing programming scripts to process small to medium size problems effectively and reliably.",
  
  "Account Receivables Data Analyst Latam", "Bayer", "São Paulo, Brasil", "Jan. 2020 - Jul. 2020",
  "Data Analysis on accounts receivables and revenues datasets, implementing pipelines from data extraction to dashboards",
  
  "Account Receivables Data Analyst", "Bayer", "São Paulo, Brasil", "Jan. 2020 - Jul. 2020",
  "Critical Participant of a diverse array of projects like the DataGis of the Credit Area and the Online Financing tool.",
  
  "Credit Analyst", "Bayer", "São Paulo, Brasil", "Set. 2019 - Dec. 2020",
  "Financial analysis of the clients credit risks",
  
  
  "Credit Analyst", "Bayer", "São Paulo, Brasil", "Set. 2019 - Dec. 2020",
  "Adhoc scripts for data analysis",
  
  
  "Credit Analyst", "Bayer", "São Paulo, Brasil", "Set. 2019 - Dec. 2020",
  "Starting the first machine learning Credit Model project",
  
  "Data Science Consultant", "Driven Consultant", "São Paulo, Brasil", "Jul. 2019 - Set. 2019",
  "Developed the time series model for Days on Hand of the client.",
  
  "Data Science Consultant", "Driven Consultant", "São Paulo, Brasil", "Jul. 2019 - Set. 2019",
  "SQL queries for model construction, adhoc analysis and dashboards.",
  
  "Trainee", "EY", "São Paulo, Brasil", "Apr. 2019 - Jun. 2019",
  "Automation of large scale accounting projects using programming scripts",
  
  
  "Trainee", "EY", "São Paulo, Brasil", "Apr. 2019 - Jun. 2019",
  "Documentation and analysis of the whole SQL pipeline, delivering business understanding",
  
  "Intern Risk Management - Reporting", "Bayer", "São Paulo, Brasil", "Jan. 2018 - Dec 2018",
  "Creation, automation and maintenance of several credit and cash flow reports",
  
  "Intern Risk Management - Reporting", "Bayer", "São Paulo, Brasil", "Jan. 2018 - Dec 2018",
  "Creation and improvement of Dashboards",
  
  "Intern Risk Management - Reporting", "Bayer", "São Paulo, Brasil", "Jan. 2018 - Dec 2018",
  "Forecasting project, using my own ensemble method of time series models to create hierachichal forecasts",
  
  
  
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Languages

## Portuguese

Native.

## English

Advanced.  

No certification, used regularly.


## German

Basic-Intermediary.  

B1 Certification

## Spanish

Basic.  

No Certification.


# Data Science Skills

Always Learning more Data Science, following blogs, reading books, doing online and on site courses, watching videos and more.

Well versed into using the tidyverse for Data Science and Statistical Inference.

Multiple projects doing time series forecasts.

Experience doing machine learning projects.

Work experience using and developing SQL queries.

Dashboard creation using Shiny and Tableau.

Working knowledge of the Git Workflow.

You can see my open source work on my Data Science blog [twosidesdata](twosidesdata.netlify.com).

# Technologies

## Programming Languages

* R
* SQL
* Python

## Dashboard Creation

* Shiny
* Tableau
* Power BI

## Office Stack

* Excel
* Power Point




