%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\colorlet{awesome}{awesome-red}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Bruno Testaguzza Carlin}{}

\position{Trainee}
\address{Ernst \& Young - São Paulo}

\mobile{+55 11 99376-5775}
\email{\href{mailto:brunotestaguzza@gmail.com}{\nolinkurl{brunotestaguzza@gmail.com}}}
\homepage{twosidesdata.netlify.com/}
\github{brunocarlin}
\linkedin{bruno-carlin-451007172}
\twitter{BrunoTestaguzza}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

% Templates for detailed entries
% Arguments: what when with where why
\usepackage{etoolbox}
\def\detaileditem#1#2#3#4#5{
\cventry{#1}{#3}{#4}{#2}{\ifx#5\empty\else{\begin{cvitems}#5\end{cvitems}}\fi}}
\def\detailedsection#1{\begin{cventries}#1\end{cventries}}

% Templates for brief entries
% Arguments: what when with
\def\briefitem#1#2#3{\cvhonor{}{#1}{#3}{#2}}
\def\briefsection#1{\begin{cvhonors}#1\end{cvhonors}}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {abril 2019}
  {Bruno Testaguzza Carlin~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\hypertarget{insper}{%
\subsection{Insper}\label{insper}}

\href{https://www.insper.edu.br/graduacao/economia/}{Graduation Economics}

2014-2018.

\hypertarget{digital-house}{%
\subsection{Digital House}\label{digital-house}}

\href{https://br.digitalhouse.com/curso/data-science/}{Studying Data Science}

\hypertarget{porto-seguro}{%
\subsection{Porto Seguro}\label{porto-seguro}}

\href{https://www.portoseguro.org.br/conteudo/detalhe/currculo-brasileiro/ensino-mdio-comrcio-exterior}{Foreign Commerce - High School}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2012}
\item
\end{enumerate}

\hypertarget{experience}{%
\section{Experience}\label{experience}}

\hypertarget{bayer}{%
\subsection{Bayer}\label{bayer}}

I have 1 year of working experience as an Intern for the Risk Managment, Reporting area in Bayer. I was responsible for the creation, automation and maintance of several credit and cash flow reports. My most remarkble skill when doing these regular tasks was combining my VBA and Excel knowledge to create and improve Dashboards.

I executed a forecasting project that involved using my own algorithm created in R to improve automatic forecasting performance of time series by ensemble models, I then hirarhical forecasts bringing information on all branches of recevables toghether, most importanly the project proved the viability of doing automated forecasts, potencially reducing working hours threfore costs.

\hypertarget{ernst-young}{%
\subsection{Ernst \& Young}\label{ernst-young}}

Trainee \href{https://www.ey.com/us/en/services/assurance/financial-accounting-advisory-services}{FAAS}.

In training.

\hypertarget{languages}{%
\section{Languages}\label{languages}}

\hypertarget{portuguese}{%
\subsection{Portuguese}\label{portuguese}}

Native.

\hypertarget{english}{%
\subsection{English}\label{english}}

Advanced.

No certification, used regularly.

\hypertarget{german}{%
\subsection{German}\label{german}}

Basic-Intermediary.

B1 Certification

\hypertarget{spanish}{%
\subsection{Spanish}\label{spanish}}

Basic.

No Certification.

\hypertarget{data-science-skills}{%
\subsection{Data Science Skills}\label{data-science-skills}}

I am an eager to learn Data Science, following blogs, reddit, reading books, doing online an on site courses, watching conference videos and more.

I am well versed into using the tidyverse for Data Analisys and Statistical Inference, with a formal background aquired in optional courses on my college.

I have studied the most about time series.

Advanced R.

Intermediary Python.

\end{document}
