---
title: 'Presentation Data Science and Decision Making 1'
authors: 
  - admin
date: '2020-05-21'
slug: exploratory-data-analysis-basics-part2
categories:
- R and Python
tags:
- R Markdown
- reticulate
- pandas
- dplyr
- modeling

subtitle: 'Using multiple packages from R and Python'
summary: 'Part of our gradution grading exercises'
output:
  blogdown::html_page:
    toc: true # table of content true
---


# Goal

Read data from Brazil's cell phone companies and predict customer satisfaction

```{r}
library(reticulate)
use_miniconda("r-reticulate",required = TRUE)
options(reticulate.repl.quiet = TRUE)

```

```{r}
file_path <- here::here()
file_path_linux <- paste(file_path,"content","post","data",sep = "/")
```



# Python

## Import libraries

```{python}
import pandas as pd
import numpy as np
```

## Read feather data frame

```{python}
df1 = pd.read_feather(r.file_path_linux + "/BD_PRE.feather")
```

## Describe the dataframe

```{python}
df1.describe()
```

## Drop features

My group read the data dictionary and glanced at the data to decido to drop of multipe features with for low variance or too high cardinality

```{python}
df1=df1.drop(["IDTNS","TIPO","DATA","H0","Q1","Q2","Q3","Q4","Q6","Q7"],axis=1)

df1.head()
```

## Rename target

```{python}
df1 = df1.rename(columns = {'J1':'Target'})
```


## NA enconding

The dictionary defined 99 as missing in multiple features 

```{python}
df2 =  df1.copy()
```

```{python}
df2['B1_1'].replace([99], np.NaN,inplace = True)
df2['B1_2'].replace([99], np.NaN,inplace = True)
df2['C1_1'].replace([99], np.NaN,inplace = True)
df2['C1_2'].replace([99], np.NaN,inplace = True)
df2['D2_1'].replace([99], np.NaN,inplace = True)
df2['D2_2'].replace([99], np.NaN,inplace = True)
df2['D2_3'].replace([99], np.NaN,inplace = True)
df2['F5'].replace([99], np.NaN,inplace = True)
df2['F4'].replace([99], np.NaN,inplace = True)
df2['F2'].replace([99], np.NaN,inplace = True)
df2['A5'].replace([99], np.NaN,inplace = True)
df2['A4'].replace([99], np.NaN,inplace = True)
df2['A3'].replace([99], np.NaN,inplace = True)
df2['A2_1'].replace([99], np.NaN,inplace = True)
df2['A2_2'].replace([99], np.NaN,inplace = True)
df2['A2_3'].replace([99], np.NaN,inplace = True)
df2['E1_1'].replace([99], np.NaN,inplace = True)
df2['E1_2'].replace([99], np.NaN,inplace = True)
df2['E1_3'].replace([99], np.NaN,inplace = True)
df2['F4'].replace([99], np.NaN,inplace = True)
df2['F5'].replace([99], np.NaN,inplace = True)
df2['F6'].replace([99], np.NaN,inplace = True)
```

Sometimes variations of missing like didn't want to answer were also enconded as numbers so we encoded those ase missing as well

```{python}
df2['Q8'].replace([999999], np.NaN,inplace = True)
df2['H1'].replace([99,99999], np.NaN,inplace = True)
df2['H2'].replace([99997,99998,99999,100000,999998,999999], np.NaN,inplace = True)
```

## Feature Engeniring

Droped H2a for now in order to code it as categories

```{python}
df2.drop(["H2a"],inplace = True,axis = 1)
```

```{python}
df3 = df2.copy()
```

```{python}
df3.loc[(df3["H2"] >=0) & (df3["H2"] <1000), "RIQUEZA"]=1
df3.loc[(df3["H2"] >=1000) & (df3["H2"] <3000), "RIQUEZA"]=2
df3.loc[(df3["H2"] >=3000) & (df3["H2"] <6000), "RIQUEZA"]=3
df3.loc[(df3["H2"] >=6000) & (df3["H2"] <10000), "RIQUEZA"]=4
df3.loc[(df3["H2"] >=10000) & (df3["H2"] <15000), "RIQUEZA"]=5
df3.loc[(df3["H2"] >=15000) & (df3["H2"] <20000), "RIQUEZA"]=6
df3.loc[(df3["H2"] >=20000), "RIQUEZA"]=7
```

```{python}
df3.RIQUEZA.value_counts(dropna =False)
```

## Target Variable

We decided with an nps system that scores above 8 were good scores, and encoded these cases as 1 and the rest as 0.

```{python}
df3['Target'].replace([99], np.NaN,inplace = True)

df3.loc[(df3["Target"] <8) ,"Target2"]= 0
df3.loc[(df3["Target"] >=8 ) ,"Target2"]= 1


df3.dropna(subset=['Target'],inplace = True)

```


Variaveis Categoricas Moda
Estado  
Operadora  
RIQUEZA  
Q9  
I1 
D1     
Q5    
F1
F3  
F5  
G1

Variaveis Categoricas Missing Explicito
A1_x

## NA imputing 

We decided that these numeric features would be imputted with 0s a more robust approach could be taken but the main idea was for to create a simple model

```{python}
df3["A1_1"].fillna(0,inplace = True)
df3["A1_2"].fillna(0,inplace = True)
df3["A1_3"].fillna(0,inplace = True)
df3["A1_4"].fillna(0,inplace = True)
df3["F1"].fillna(0,inplace = True)
df3["F3"].fillna(0,inplace = True)
df3["F5"].fillna(0,inplace = True)
```

## Feature encoding

We originally hand encoded all the features in python, this would help to automate the predictions latter down the pipe
unfortunally when replicating the code it seems I have a bug on reticulate so I will do that in r instead

```{python}
# df3 = df3.astype({'Q9': 'category'})
# df3 = df3.astype({'I1': 'category'})
# df3 = df3.astype({'D1': 'category'})
# df3 = df3.astype({'Q5': 'category'})
# df3 = df3.astype({'F1': 'category'})
# df3 = df3.astype({'F3': 'category'})
# df3 = df3.astype({'F5': 'category'})
# df3 = df3.astype({'G1': 'category'})
# df3 = df3.astype({'A1_1': 'category'})
# df3 = df3.astype({'A1_2': 'category'})
# df3 = df3.astype({'A1_3': 'category'})
# df3 = df3.astype({'A1_4': 'category'})
# df3 = df3.astype({'RIQUEZA': 'category'})
# df3 = df3.astype({'Target2': 'category'})
```


```{python}
df3.dtypes
```

## Prepare df to export to r


```{python}
df4=df3.loc[:,['Q5','Q8','Q8a','Q9','B1_1','B1_2','C1_1','C1_2','D1','D2_1','D2_2','D2_3','E1_1','E1_2','E1_3','A1_1','A1_2','A1_3','A1_4','F1','F3','F5','G1','H1','I1','PESO','RIQUEZA',"Target2"]]
```



#  R

## Import df from python

```{r}
df_r <- py$df4
```

## Import libraries


```{r,results='hide'}
library(DataExplorer)
library(tidyverse)
library(tidymodels)
library(furrr)
library(h2o)
library(DALEX)
library(DALEXtra)
library(iBreakDown)
library(ingredients)
library(probably)
```

## Encode types


```{r}
df_r %>% glimpse()
```

```{r}
category_pipe <- . %>% 
  as.character() %>% 
  if_else(. == "NaN",NA_character_,.) %>% 
  as_factor()
```

```{r}
df_r <- df_r %>% 
  mutate_at(vars(Q9,I1,D1,Q5,F1,F3,F5,G1,starts_with("A1"),RIQUEZA,Target2),.funs = category_pipe)
```


## Explore in r with data explorer

```{r}
DataExplorer::introduce(df_r)
```

```{r}
DataExplorer::plot_intro(df_r)
```

```{r}
plot_missing(df_r)
```
## Drop features


```{r}
df_r <- df_r %>% 
  select(-starts_with("D2"))
```

```{r}
plot_missing(df_r)
```
## Encode response in r

```{r}
  df_r <- df_r %>% 
  rename(response = Target2) %>% 
  select(-PESO)
```



## More exploration

```{r}
df_r %>%
  mutate(response = response %>% fct_recode(bad = "0",good ="1")) %>% 
  count(response) %>%
  ggplot(aes(response, n, fill = response)) + 
  geom_col(width = .5, show.legend = FALSE) + 
  scale_y_continuous(labels = scales::comma) +
  scale_fill_manual(values = c("red","blue")) +
  labs(
    x = NULL,
    y = NULL,
    title = "Distribution of cases"
  )
  
```
# Modeling

## Train test split

```{r}
telefone_initial_split <- df_r %>% rsample::initial_split(prop = 0.9)
telefone_initial_split
```

```{r}
train_data <- training(telefone_initial_split)
test_data <- testing(telefone_initial_split)
```


## Recipe for models

```{r}
recipe_telefone <- 
  recipe(response ~.,data = train_data) %>%
  #step_upsample(response,skip = TRUE) %>% 
  step_modeimpute(all_predictors(),-all_numeric()) %>% 
  step_medianimpute(all_predictors(),-all_nominal()) %>% 
  step_normalize(all_numeric()) %>% 
  step_rm(RIQUEZA)
  #step_dummy(all_predictors(),-all_numeric())
```

## Prep Data

```{r}
simple_model_recipe <- recipe_telefone %>%
  prep(retain = TRUE)

simple_train <- simple_model_recipe %>% juice()

simple_test <- simple_model_recipe %>% bake(test_data)

```


## Logistic Regression

```{r,results='hide'}


logistic_regression <- 
  logistic_reg(mode = "classification",penalty = 0) %>%
  set_engine("glmnet") %>% 
  fit(response ~.,data = simple_train)

metrics_log_reg <- logistic_regression %>% 
  predict(simple_test) %>% 
  bind_cols(simple_test %>% select(response)) %>% 
  metrics(truth = response,estimate = .pred_class)

metrics_roc_auc <- logistic_regression %>% 
  predict(simple_test,type = "prob") %>% 
  bind_cols(simple_test %>% select(response)) %>% 
  roc_auc(truth = response,predictor =.pred_0)
```

### Metrics Logistic

```{r}
metrics_log_reg
```

```{r}
metrics_roc_auc
```

I am going to keep using roc from now on
## Lasso

```{r}
lasso_regression <- logistic_reg(mode = "classification",mixture = 0) %>% 
  set_engine("glmnet") %>% 
  fit(response~ .,data = simple_train)

lasso_roc_auc_cv <- lasso_regression %>% 
  multi_predict(new_data = simple_test,type = "prob") %>% 
  bind_cols(simple_test) %>%
  unnest() %>% 
  group_by(penalty) %>% 
  do(ok = roc_auc(.,truth = response,predictor = .pred_0)) %>% 
  unnest() %>%
  spread(key = .metric,value = .estimate) %>%
  arrange(roc_auc %>% desc)
```

### Metrics Lasso 

```{r}
lasso_roc_auc_cv
```


## Ridge

```{r}
ridge_regression <- logistic_reg(mode = "classification",mixture = 1) %>% 
  set_engine("glmnet") %>% 
  fit(response~ .,data = simple_train)

ridge_results_cv <- ridge_regression %>% 
  multi_predict(new_data = simple_test,type = "prob") %>% 
  bind_cols(simple_test) %>%
  unnest() %>% 
  group_by(penalty) %>% 
  do(ok = roc_auc(.,truth = response,predictor = .pred_0)) %>% 
  unnest() %>%
  spread(key = .metric,value = .estimate) %>%
  arrange(roc_auc %>% desc)
```

### Metrics Ridge

```{r}
ridge_results_cv
```

## Random Forest

```{r}
  random_forest <- rand_forest(mode = "classification",trees = 100) %>% 
  set_engine("ranger") %>% 
  fit(response~ .,data = simple_train)
```

### Metrics Random forest

The best model currently

```{r}
random_forest %>% 
  predict(simple_test,type = "prob") %>% 
  bind_cols(simple_test %>% select(response)) %>% 
  roc_auc(truth = response,predictor =.pred_0)
```

## h2o

h2o is usually very fast but not fast enough for this blogpost but here is the code for it

### Start CLuster


```{r eval=FALSE, include=FALSE}
# number_cores <- parallel::detectCores()/2
# h2o.init(nthreads = number_cores)
```


### Upload df's

```{r}
# simple_train_hex <-  as.h2o(simple_train)
# simple_test_hex = as.h2o(simple_test)
# simple_y_hex <- simple_train %>% select(response) %>% pull %>% as.numeric()
# simple_x_hex <- simple_train %>% select(-response)
```

### Fit auto ml

With a 2 minutes timer

```{r,results='hide'}
# h2o.no_progress()
# 
# aml <- h2o.automl(y = "response",
#                   training_frame = simple_train_hex,
#                   max_runtime_secs = 120,
#                   seed = 1)
# 
```

### Model results


```{r,results='hide'}
# pred <- h2o.predict(aml, simple_test_hex)
```



```{r}
# aml@leaderboard
```

```{r}
# model_ids <- as.data.frame(aml@leaderboard$model_id)[,1]
# model_ids
```

### Using a stacked model

```{r}
# best_h2o <- h2o.getModel(model_ids[model_ids %>% str_detect("StackedEnsemble_BestOfFamily_AutoML")])
```

### Performance

```{r,results='hide'}
# result_predictions <- predict(best_h2o,simple_test_hex)
```

```{r}
# result_predictions %>% 
#   as_tibble() %>% 
#   bind_cols(simple_test) %>% 
#   roc_auc(truth = response,predictor = p0)
```


# DALEX - Are machinge learning models Black Boxes?

Code based from [Dalex page](https://github.com/ModelOriented/DALEX)

## Dalex X e Y

```{r}
x_dalex <- simple_test %>% select(-response)
y_dalex <- simple_test %>%
  transmute(response = response %>%
              as.numeric()) %>% 
  mutate(response = if_else(response == 1,
                            0,
                            1)) %>% as.data.frame()
y_dalex <- y_dalex[,1]
```

## Model Explainer

```{r,results='hide'}
explainer_log_reg <- DALEX::explain(logistic_regression, data=x_dalex, y=y_dalex, label="logistic_reg")
explainer_rf <- explain(random_forest,x_dalex,y_dalex,label ="random_forest")
```
## Feature Importance

```{r}
mp_log_reg <- model_parts(explainer_log_reg)
mp_rf <- model_parts(explainer_rf)
```

```{r}
plot(mp_log_reg,mp_rf)
```


## Variable explanation

### Accumulated Local Effects Profiles aka ALEPlots

B1_2: Note in regards to how well the company has delivered on its publicity.

```{r,results='hide'}
adp_log_reg <- accumulated_dependence(explainer_log_reg,variables = "B1_2")
adp_rf <- accumulated_dependence(explainer_rf,variables = "B1_2")
```

```{r}
plot(adp_log_reg,adp_rf)
```


### Factor explanation

G1: Does another company exist that is serving the same area:

1. Yes
2. No
3. Don't know


```{r,results='hide'}
expl_log_reg <- accumulated_dependence(explainer_log_reg,variables = "G1", variable_type = "categorical")
expl_rf<- accumulated_dependence(explainer_rf,variables = "G1", variable_type = "categorical")
```

```{r}
plot(expl_log_reg,expl_rf)
```


## Single prediction explanation 

Only the first case 


```{r,results='hide'}
bd_log_reg <- predict_parts(explainer_log_reg, x_dalex[1,])
bd_rf <- predict_parts(explainer_rf, x_dalex[1,])
```


Logistic Regression
```{r}
plot(bd_log_reg)
```
Random Forest

```{r}
plot(bd_rf)
```

Not the coolest graph since unfortunately we use a normalization process, maybe in the future with the workflows package we can see better graphs