---
title: FizzBuzz in the tidyverse
author: 
- admin
date: '2019-12-22'
slug: fizzbuzz-in-the-tidyverse
categories:
  - r-project
tags:
  - tidyverse
  - programming
image:
  caption: ''
  focal_point: ''
---




FizzBuzz is and old kids games

Not that popular where I am from Brazil, Fizz Buzz has a simple set of rules

You start counting from 1 (obviously) and when a number is a multiple of 3 you say **Fizz**,  
if the number is a multiple of 5 you say  **Buzz**,  
and if the number is a multiple of both you shout **FizzBuzz**,
And for every other case you can say the **number itself**, simple right?

I watched this really cool video on Tom Scott channel and realized that I have never attempted this problem as a programmer

This is an blog post full of tricks I will try to point them all out.

[Scott's video](https://youtu.be/QPZ0pIK_wsc)

# Naive FizzBuzz

[Naive FizzBuzz](https://www.r-bloggers.com/fizzbuzz-in-r-and-python/)

```{r Naive FizzBuzz}
for (i in 1:15){
  
  if(i%%3 == 0 & i%%5 == 0) {
    print('FizzBuzz')
  }
  else if(i%%3 == 0) {
    print('Fizz')
  }
  else if (i%%5 == 0){
    print('Buzz')
  }
  else {
    print(i)
  }
  
}
```

1. Simple flow control with if, else statements
2. Some basic operators ($, ==)

# Extending the loop approach

Using Scott's approach we can improve a bit on the logic

```{r Scott FizzBuzz}
for (i in 1:15){
  current_out <- ''
  if(i%%3 == 0) {
    current_out <- paste0(current_out,'Fizz')
  }
  if (i%%5 == 0){
    current_out <- paste0(current_out,'Buzz')
  }
  if (current_out == ''){
    print(i)
  }
  else print(current_out)
}
```

While it is possible to improve open this loop, I think it already is close to the limits of what I would call a very simple example

# Functional approach

Thanks [Functional FizzBuzz](https://www.r-bloggers.com/fizzbuzz-in-r/)

```{r}
divisor <-
  function(number, string) {
    function(d) {
      if (d %% number == 0) string else ""
    }
  }

mod3er <- divisor(3, "Fizz")
mod5er <- divisor(5, "Buzz")

fizzbuzz <- 
  function(i) {
    res <- paste0(mod3er(i), mod5er(i))
    ifelse(res == "", i, res)
  }

sapply(1:15, fizzbuzz)
```

So enumerating the new concepts here:

1. Functions that create functions (mod3er,mod5er)
2. Functions that create functions that create functions (divisor)
3. Applying functions (sapply)
4. Functional if else (I prefer it)

All of which seen pretty complicated at first but will pay off big time latter.

# My approach (tidyverse)

## The Basics

Loading the tidyverse

```{r}
library(tidyverse)
```

```{r Basic Tidyverse}
divisor <- function(number, string) {
    function(input) {
      if_else(condition = input %% number == 0,
              true = string,
              false = "")
    }
}

mod3 <- divisor(3, "Fizz")
mod5 <- divisor(5, "Buzz")

list_functions <- list(mod3,mod5)

mapper_list <- function(i,list_functions) map(list_functions, exec,i)

map(1:15,mapper_list,list_functions) %>% 
  map(reduce,str_c)
```

We learned two new tricks:

1. Executing a list of functions using exec
2. reducing an list



## Making just one call

```{r Ellipsis Tidyverse}
fancy <- function(i,...) {
  list_functions <- list(...)
  mapper_list <- function(i,list_functions) map(list_functions, exec,i)
  map(i,mapper_list,list_functions) %>%
  map(reduce,str_c)
}

fancy(1:15,mod3,mod5)
```

One new trick using ellipsis

## Or preparing for an api

```{r API Tidyverse}
api_less_fancy <- function(i,list_functions) {
  mapper_list <- function(i,list_functions) map(list_functions, exec,i)
  map(i,mapper_list,list_functions) %>%
  map(reduce,str_c)
}

api_less_fancy(1:15,list(mod3,mod5))
```

# Extending FizzBuzz

Let's see how easy it is too make the game more difficult:

## Changing names

```{r}
mod3n <- divisor(3, "Buzz")
mod5n <- divisor(5,'Fizz')
fancy(1:15,mod3n,mod5n)
```


## Adding divisors

```{r}
mod2 <- divisor(2, "Deuce")
fancy(1:30,mod2,mod3,mod5)
```

## Adding new rules

```{r}
less <- function(number, string) {
    function(input) {
      if_else(condition = input < number,
              true = string,
              false = "")
    }
}
```

```{r}
less10 <- less(10,"Small")
```

```{r}
fancy(1:15,less10,mod3,mod5)
```

That is it have a great day.

